\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage{array}
\usepackage{hyperref}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\hypersetup{hidelinks}

\begin{document}

\title{A Governed Public-Data Benchmark of Quantum Machine Learning for Human-Rated Cislunar Trajectory-Correction Planning}
\titlerunning{A Governed QML Benchmark for Cislunar Trajectory Correction}

\author{Taechasith Kangkhuntod}
\authorrunning{T. Kangkhuntod}
\institute{University of the Thai Chamber of Commerce, Bangkok, Thailand}

\maketitle

\begin{abstract}
This research asks whether quantum-kernel models add predictive value to a
public-data, human-rated cislunar trajectory-correction decision-support
benchmark when compared fairly with physics-based controls. The
study froze its source-bound simulator, grouped development splits, fold-local
preprocessing, retention rules, and claim boundary before model outcomes were
reported. The simulator credibility chain accepted 67 eligible public-data
checks with zero failures. The preregistered Q01 fidelity-style quantum kernel
had mean normalized root-mean-square error (NRMSE) 0.646614, compared with
0.008739 for the C06 physics-residual control; no regime qualified for advance.
The projected Q01b successor had NRMSE 0.661207 versus 0.006833 for C06. A
feasibility-only quantum kernel reached recall 0.108860 at the frozen threshold,
which was inadequate for its safety-filter interpretation. Sixteen further,
prospectively bounded development-only candidates completed as valid negatives;
the strongest apparent residual gain did not survive its matched classical
control. The finding is not that QML is universally ineffective. It is that the
tested QML representations did not justify additional complexity for this
frozen task and control set. The societal contribution is a transparent method
for preventing unsupported AI claims from being promoted into high-consequence
human decision contexts: preserve source provenance, show negative outcomes,
and keep crew-related requirements and human review separate from a model score.
This study does not claim quantum advantage, propellant savings, mission-loop
validity, flight readiness, hardware performance, or a new QML invention.
\keywords{Quantum machine learning \and human-centered AI \and decision support \and cislunar trajectory design \and reproducible benchmarking \and negative results}
\end{abstract}

\input{sections/01_introduction}
\input{sections/02_scope}
\input{sections/03_related_work}
\input{sections/04_methods}
\input{sections/05_results}
\input{sections/06_discussion}
\input{sections/07_limitations}
\input{sections/08_future_boundary}
\input{sections/09_availability}
\input{sections/10_conclusion}

\begin{credits}
\subsubsection{\ackname}
Reserved for an advisor contribution statement, pending advisor review.
\end{credits}

\input{sections/A_reproducibility}
\input{sections/B_literature_audit}

\bibliographystyle{splncs04}
\bibliography{references}

\end{document}
