\section{Related Work and Positioning}

The target problem is positioned relative to public work on Artemis
trajectory-correction design, rather than being presented as a replacement for
mission-owned analysis. Woffinden et al. describe a correction-burn placement
formulation that incorporates uncertainty, crew-related timing, and entry
constraints \cite{woffinden2023}. Classical learning research has explored
low-thrust guidance and cislunar transfer design, but those settings differ in
dynamics, propulsion, objectives, and validation structure
\cite{zavoli2020,sullivan2021,izzo2021,steffen2025,xie2022,zhang2025}. They
are valuable precedents for surrogate modeling, low-fidelity references,
cost--reachability endpoints, and retaining infeasible cases, not
interchangeable baselines for a human-rated correction benchmark.

Quantum feature-space methods express a classical input through an encoding
and compare encoded states by a quantum-derived similarity
\cite{schuld2019,havlicek2019}. The method can be used in a kernel learner,
but its predictive value depends on an alignment between the data geometry,
the feature map, the measurement, and the task. Theoretical and numerical work
has made this caveat increasingly explicit: hard-to-simulate circuits do not
automatically give a learning advantage, and the data distribution can make a
classical approximation competitive \cite{huang2021,sweke2025}.

The present work is particularly informed by three benchmarking lessons. First,
kernel bandwidth and encoding scale are part of the effective inductive bias,
not negligible implementation details \cite{shaydulin2022}. Second, a
quantum-kernel study should include appropriately strong classical
counterparts, including random features where relevant
\cite{otten2020,rahimi2007,sweke2025}. Third, a comparison should report more than its
best run: model choice, split structure, seed variation, capacity, and
post-outcome choices all affect what a claimed gain means
\cite{bowles2024,schnabel2024,pernot2020}.

\subsection{Literature provenance of the frozen protocol}

The literature set was used to shape the protocol, not to claim that every
reviewed model was executed. Data re-uploading, encoding-dependent
generalization, and initialization studies informed the need to freeze
encoding, observables, initialization, and seed handling
\cite{perez2020,caro2021,grant2019}. Quantum-agent work informed the need for
matched classical capacity and explicit readout choices, but it did not turn
this supervised benchmark into a reinforcement-learning study
\cite{skolik2022}. Quantum annealing for trajectory transcription was retained
as adjacent quantum-optimization context and deliberately excluded from the
QML candidate set \cite{degrossi2025}.

The accompanying literature-source audit accounts for all 23 accepted records
used in the experiment's review package and additionally identifies the
random-Fourier source behind the A01 control. It distinguishes direct
methodological influence from an empirical comparison in this paper. This
prevents a citation from being mistaken for evidence that a reviewed external
method was reproduced, validated, or outperformed here.

This paper does not make an exhaustive literature-review claim. The repository
preserves a bounded extraction set of 23 accepted records used to establish the
initial protocol and a separate archival discovery refresh. The refresh did
not change the experiment, thresholds, figures, or outcomes. Literature is
therefore used here to position the benchmark and justify controls, not to
construct a retrospective theory of success.
