\section{Discussion}
\label{sec:discussion}

The principal finding is a controlled negative benchmark: the runs completed
validly, but the tested performance hypotheses were rejected. The Q01
fidelity-style quantum kernel was far behind the physics-residual control, the
Q01b projected feature map did not close the gap, and the feasibility-only
kernel did not meet its fixed multi-metric screening criteria. The successor
branch exposes a further failure mode: a candidate can improve over one
baseline yet fail against a classical model with the same staged construction.
This is why matched dequantization controls and thresholds fixed before
outcomes belong in the protocol.

The negative conclusion is deliberately narrow. It concerns the tested feature
maps and successor constructions under this public-data scenario generator,
grouped development procedure, resource envelope, and comparator set. It does
not rule out all QML, all cislunar machine learning, or all future quantum
hardware. Broader claims would require new tasks, preregistration, scaling and
noise studies, hardware measurements, and appropriate classical resource
comparisons.

\subsection{Human--AI interaction contribution for mission planning}

For a human--AI interaction setting, this paper contributes an evidence design
for decision support, not an autonomous navigation method or a user-tested
interface. A model output should be considered only after a qualified analyst
can inspect what was modeled, what data and conditions were in scope, which
alternatives were tested, and why the result did or did not advance. This
supports the goal of appropriate reliance on automation rather than either
uncritical acceptance or blanket rejection \cite{lee2004}.

The protocol operationalizes that goal through four inspectable elements:
an intended-use and source boundary; controls that can falsify a
model-specific explanation; status records for valid negatives, ineligible
paths, and source-ineligible events; and an explicit human-authorization
boundary. These elements do not make an output more accurate. They make its
evidential status reviewable before it is discussed as support for a planning
decision. This framing is compatible with human--AI interaction guidance that
treats a system's capabilities and limitations as design material rather than
as details hidden behind a prediction \cite{amershi2019}.

A future cislunar planning tool should therefore present a compact evidence
record alongside any candidate correction: the model and data scope, relevant
comparators, uncertainty and failure conditions, gate status, and the action
that remains available to the human reviewer. It should not reduce Q01, Q01b,
and FQK to a single red or green signal. In particular, Q02 and Q03 are
\texttt{not\_reached\_under\_frozen\_eligibility}, not failed experiments:
their first-rung tasks ran correctly, but they were ineligible for larger-rung
computation under a rule fixed before results. Retaining that distinction makes
the evidence ledger more truthful and prevents a later analyst from inventing
a selection path that never existed.

These are design implications, not empirical HCI findings. The present study
did not observe planners, measure workload or situation awareness, or test
whether an evidence display improves comprehension or calibrated reliance.
Those questions require a separate evaluation with intended users and mission
analysts. The contribution here is the auditable information that such an
evaluation should make perceptible.

\subsection{Implications for QML benchmarking}

The physics-residual control is a key methodological result. A generic
classical baseline is insufficient when a low-fidelity model can directly
represent part of the target structure. In this benchmark, that residual
structure was more informative than the tested quantum fidelity features. This
does not establish a theorem about quantum circuits; it is a task-specific
comparison of inductive bias that future proposals must beat fairly.

The QML literature has repeatedly shown that benchmark conclusions depend on
which classical methods are available to the comparison
\cite{bowles2024,schnabel2024}. D046 gives a concrete trajectory example.
Compared only with C06, its raw 5.80\% reduction could appear promising. A
matched TWO-RBF control explains enough of that difference that D046 fails the
predeclared 5\% rule. The relevant question is therefore not ``is the
candidate better than one baseline?'' but ``does its incremental mechanism
remain supported when a classical model receives the same residual
construction?''

The matched control is not claimed to be a universally best classical model.
It removes one credible alternative explanation for the purported QML effect.
This is a transferable lesson for human-facing space AI: an appealing model
description is not enough for an operator or reviewer to infer that the model
adds decision-relevant value.

\subsection{Safety objective as a distinct scientific question}

The FQK and CSAFE-RF records show why predictive metrics must be connected to
both label meaning and intended action. Here, the positive label is feasible.
AUROC measures ranking, Brier score probability error, and recall the share of
actually feasible options retained. Precision and false-positive rate address
the separate risk of admitting an actually infeasible option. FQK remains
negative under its frozen multi-metric rule even though its AUROC is above
random, because its Brier score and feasible-case recall did not match the
classical controls. Selecting only the most favorable metric after inspection
would conceal this limitation.

The higher-recall classical result is not a rescue or a safety result. It is a
future design lesson: a screening protocol should specify before fitting a
minimum feasible-case recall for usefulness, a maximum infeasible-case
false-positive rate for protection, a calibration requirement, and the action
taken when the model abstains. Those quantities cannot be replaced by one
``safety'' score. Testing such a policy requires a separately authorized
experiment; using it to alter Gate 5 after inspection would invalidate the
original test.
