\section{Limitations and Threats to Validity}
\label{sec:limitations}

First, the study is public-data and development-only. Calibration and
final-test data were not read. The paper cannot estimate final-test error,
operational calibration, mission-loop behavior, propellant savings, or flight
readiness. The use of Artemis-related public work establishes relevance of the
problem framing, not access to mission-owned truth data or authority to draw
mission conclusions.

Second, simulator agreement is bounded. The Gate 3 results support the
eligible public endpoint comparisons, but they do not validate every force
model, contingency, navigation product, or human-rating consideration. RTC3
is source-ineligible, and some generated scenario decisions do not have an
independently feasible numerical reference. Those limitations remain in the
dataset rather than being removed after model results are observed.

Third, the quantum experiments are small-qubit classical statevector
simulations within a laptop-bounded resource envelope. They do not report shot
noise, gate noise, device connectivity, state-preparation latency,
transpilation cost, hardware calibration, or end-to-end quantum runtime. They
cannot demonstrate quantum speedup, hardware efficiency, or a practical
quantum advantage. An alleged advantage would require all of those questions
to be addressed against a fair classical resource baseline.

Fourth, the methods are limited by their frozen design. The chosen
preprocessing, feature maps, sample rungs, controls, and thresholds make the
comparison interpretable but restrict the scope of inference. A different
method can be scientifically tested only through a new protocol, not by
modifying the completed campaign until a favorable result appears.

Finally, the literature synthesis is bounded, not systematic. The inclusion
set provides methodological context and control requirements but does not
prove that no related method exists. This is why the paper makes a benchmark
claim rather than a novelty or universal-performance claim.
